### 2013-09-18 chi2014/method.tex
fix quotes in method section

\begin{enumerate}
    \item "Storage Container"
    \item "Small Storage Box"
    \item "Coin Storage"
    \item "Travel Jewelry Case"
\end{enumerate}

@@

Initially, a coding scheme was employed in which a master list of unique ideas was formed, and each response was assigned a categorical code from this list. It proved difficult to determine and adhere to a constant granularity of distinction. For example, it is desireable to encode some equality between "use [MP3 players] to build a chair, and "use [MP3 players] to build a table". Information loss results from either assigning both the same code or each different codes. An interval specificity scale is also difficult to employ; intuitively, we cannot compare the distance between "audiobooks" and "audio books for the blind" with the distance between the latter and "[audio] instructions for the blind on a variety of things".

>>>>

\begin{enumerate}
    \item ``Storage Container"
    \item ``Small Storage Box"
    \item ``Coin Storage"
    \item ``Travel Jewelry Case"
\end{enumerate}

@@

Initially, a coding scheme was employed in which a master list of unique ideas was formed, and each response was assigned a categorical code from this list. It proved difficult to determine and adhere to a constant granularity of distinction. For example, it is desireable to encode some equality between ``use [MP3 players] to build a chair, and "use [MP3 players] to build a table". Information loss results from either assigning both the same code or each different codes. An interval specificity scale is also difficult to employ; intuitively, we cannot compare the distance between ``audiobooks" and ``audio books for the blind" with the distance between the latter and ``[audio] instructions for the blind on a variety of things".
